\huge Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence $^{*}$\footnoterule\thanks{$^{*}$This work is partially supported by NSF Grant RI-Medium: \#IIS-1162095 to }

### 2015-04-29 Tex_AXYB/paper.tex
changed folder names to be Matlab_AXYB & Tex_AXYB

%\usepackage{amsmath}   % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
\usepackage{multirow}
\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
\setlength{\columnsep}{0.24in}
% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}

@@

While the cloud of frames ${A_{i}}$ is clustered around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008}.

\begin{equation}\label{equ13}
    ^{k+1}M_{A} = ^{k}M_{A} \circ exp[\frac{1}{n}\sum_{i=1}^{n}log(^{k}M_{A}^{-1}\circ A_{i})]
\end{equation}

An initial estimate of the iterative procedure can be $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$,then the process iterates until the cost function, $\parallel \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) \parallel^{2}$ falls below a predefined threshold, where the cost function is minimized and the minimum defines $M_{A}$. A similar procedure is used for computing $M_B$.

The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly focused functions, $f_{1}$ and $f_{2}$ can be computed as

\begin{IEEEeqnarray}{l}\label{equ14}
M_{1 \ast 2} = M_{1}M_{2} \IEEEyessubnumber
\\*
\Sigma_{1 \ast 2} = Ad(M_{2}^{-1})\Sigma_{1}Ad^{T}(M_{2}^{-1}) + \Sigma_{2} \IEEEyessubnumber
\end{IEEEeqnarray}

where

$$Ad(g)=\left(
               \begin{array}{cc}
                 R & O \\
                 \hat{t}R & R \\
               \end{array}
             \right)$$

Due to $X$ and $Y$ is fixed, as for $\delta_{X}(g)$ and $\delta_{Y}(g)$, mean and covariance are $M_{X}=X$,$\Sigma_{X}=0$ and $M_{Y}=Y$,$\Sigma_{Y}=0$, respectively, therefore we can obtain

@@

\begin{equation}\label{equ19}
\Omega= \left(
\begin{array}{ccc}
\left( \begin{array}{ccc}
       1 & 0 & 0 \\
       0 & 1 & 0 \\
       0 & 0 & 1 \\
\end{array} \right),&
\left( \begin{array}{ccc}
       -1 & 0 & 0 \\
       0 & -1 & 0 \\
       0 & 0 & 1 \\
\end{array} \right)
\\
\left( \begin{array}{ccc}
       -1 & 0 & 0 \\
       0 & 1 & 0 \\
       0 & 0 & -1 \\
\end{array} \right),&
\left( \begin{array}{ccc}
       1 & 0 & 0 \\
       0 & -1 & 0 \\
       0 & 0 & -1 \\
\end{array} \right)
\end{array}
\right)
\end{equation}

>>>>

%\usepackage{amsmath}   % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
\usepackage{multirow}
\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
\usepackage{amsmath}
\setlength{\columnsep}{0.24in}
% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}

@@

For the case where $\{A_{i}\}$ is clustered around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008} as:

\begin{equation}\label{equ13}
    ^{k+1}M_{A} = ^{k}M_{A} \circ exp[\frac{1}{n}\sum_{i=1}^{n}log(^{k}M_{A}^{-1}\circ A_{i})].
\end{equation}

An initial estimate of $M_{A}$ can be calculated as $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$, then iterations will be performed according to Eq.(\ref{equ13}) until the cost function $\parallel \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) \parallel^{2}$ falls below a predefined threshold. A similar procedure is used for computing $M_B$.

The mean and covariance for the convolution of two highly focused pdf $(f_{1} \ast f_{2})(H)$ can be computed as:

\begin{IEEEeqnarray}{l}\label{equ14}
M_{1 \ast 2} = M_{1}M_{2} \IEEEyessubnumber
\\*
\Sigma_{1 \ast 2} = Ad(M_{2}^{-1})\Sigma_{1}Ad^{T}(M_{2}^{-1}) + \Sigma_{2} \IEEEyessubnumber
\end{IEEEeqnarray}
where

$$Ad(H)=\left(
               \begin{array}{cc}
                 R & O \\
                 \hat{t}R & R \\
               \end{array}
             \right).$$

Because $X$ and $Y$ is fixed, the means and covariances for $\delta_{X}(H)$ and $\delta_{Y}(H)$ are $M_{X}=X$, $\Sigma_{X}=0$ and $M_{Y}=Y$, $\Sigma_{Y}=0$ respectively. Therefore, we can obtain

@@

%\begin{equation}\label{equ19}
%\Omega= \left(
%\begin{array}{ccc}
%\left( \begin{array}{ccc}
%       1 & 0 & 0 \\
%       0 & 1 & 0 \\
%       0 & 0 & 1 \\
%\end{array} \right),&
%\left( \begin{array}{ccc}
%       -1 & 0 & 0 \\
%       0 & -1 & 0 \\
%       0 & 0 & 1 \\
%\end{array} \right)
%\\
%\left( \begin{array}{ccc}
%       -1 & 0 & 0 \\
%       0 & 1 & 0 \\
%       0 & 0 & -1 \\
%\end{array} \right),&
%\left( \begin{array}{ccc}
%       1 & 0 & 0 \\
%       0 & -1 & 0 \\
%       0 & 0 & -1 \\
%\end{array} \right)
%\end{array}
%\right)
%\end{equation}

\begin{equation}\label{equ19}
\begin{split}
{\cal Q} = \left\{ \left(\begin{array}{ccc}
1\,\, & 0 \,\, & 0 \,\, \\
0 & 1 & 0\\
0 & 0 & 1 \end{array}\right) , \left(\begin{array}{ccc}
-1 & 0 & 0 \\
0 & -1 & 0\\
0 & 0 & 1 \end{array}\right), \right.\\
\left. \left(\begin{array}{ccc}
-1 & 0 & 0 \\
0 & 1 & 0\\
0 & 0 & -1 \end{array}\right), \left(\begin{array}{ccc}
1 & 0 & 0 \\
0 & -1 & 0\\
0 & 0 & -1 \end{array}\right)\right\}
\end{split} 
\end{equation}
